Comparing MTurk and the US Population's Occupational Diversity

### 2018-11-30 Manuscript.Rmd

In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`). In sample one (n~1~ =`r nrow(LATech)`), occupational data was self-reported by participants who were asked to described their job title. They were then brought to ONET online and asked to retrieve the  six-digit occupational classification code that most closely corresponded to their job title. In the sample two (n~2~ = `r nrow(UGA)`), participants again self-reported their job title. However, the six-digit occupational classification codes were obtained by training research assistants to match the self-reported job titles to those in the ONET database. Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation as described by Table 1. Data were again collected in 2017 as part of a separate investigation. In this sample, participants were asked to self-report their occupational data in the manner consistent with sample 1. 
```{r Table 1, results="asis"}
papaja::apa_table(table, 
                  caption = "Proportions of individuals sampled from each intermediate occupational category in 2015.",
                  landscape = TRUE,
                  note = "n = sample; 1 or 2 = sample 1 or 2, accordingly; LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
```

## Analysis

@@

# Plot data
ggplot(barplot_data, aes(Occupations, Values, fill = Group, ymax = upper, ymin = lower)) + 
  geom_bar(stat="identity", position = "dodge", width = 0.7) +
  geom_bar(stat="identity", position = "dodge", 
                colour = "black", width = 0.7, 
                show.legend = TRUE) +
  scale_y_continuous(breaks = seq(0, 0.30, 0.1), 
                limits = c(0, 0.30), 
                expand = c(0, 0)) +
  scale_fill_manual(name = "Groups" , 
                 values = c('grey30', 'grey60', 'grey 80'), 
                 labels = c("BLS 2015", "Sample 1", "Sample 2")) +
  geom_errorbar(position=position_dodge(width=0.7), 
                     width=0.0, size=0.5, color="black") +
  #ggtitle("Occupational Diversity of MTurk") +
  labs(x = element_blank(), y = "Proportions") +
  theme(legend.position = c(.8,.8), 
        #plot.title = element_text(hjust = 0), 
        text=element_text(family="serif")) +
  coord_flip()
```
## 2015 Demographic Analysis 
## Study 1 Age
```{r}
#Load BLS Data
BLS_age_15 <- read_excel("BLS.Age.2015.xlsx")

>>>>

In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`). In sample one (n~1~ =`r nrow(LATech)`), occupational data was self-reported by participants who were asked to described their job title. They were then brought to ONET online and asked to retrieve the  six-digit occupational classification code that most closely corresponded to their job title. In the sample two (n~2~ = `r nrow(UGA)`), participants again self-reported their job title. However, the six-digit occupational classification codes were obtained by training research assistants to match the self-reported job titles to those in the ONET database. Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation as described by Table 1. Data were again collected in 2017 as part of a separate investigation. In this sample, participants were asked to self-report their occupational data in the manner consistent with sample 1. 
```{r Table 1, results="asis"}
papaja::apa_table(table, 
                  caption = "Proportions of individuals sampled from each intermediate occupational category in 2015.",
                  landscape = TRUE,
                  note = "n = sample; 1 or 2 = sample 1 or 2, accordingly; LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
```
## Analysis

@@

# Plot data
ggplot(barplot_data, aes(Occupations, Values, fill = Group, ymax = upper, ymin = lower)) + 
  geom_bar(stat="identity", position = "dodge", width = 0.7) +
  geom_bar(stat="identity", position = "dodge", 
                colour = "black", width = 0.7, 
                show.legend = TRUE) +
  scale_y_continuous(breaks = seq(0, 0.30, 0.1), 
                limits = c(0, 0.30), 
                expand = c(0, 0)) +
  scale_fill_manual(name = "Groups" , 
                 values = c('grey30', 'grey60', 'grey 80'), 
                 labels = c("BLS 2015", "Sample 1", "Sample 2")) +
  geom_errorbar(position=position_dodge(width=0.7), 
                     width=0.0, size=0.5, color="black") +
  #ggtitle("Occupational Diversity of MTurk") +
  labs(x = element_blank(), y = "Proportions") +
  theme(legend.position = c(.8,.8), 
        #plot.title = element_text(hjust = 0), 
        text=element_text(family="serif")) +
  coord_flip()
```
## 2015 Demographic Analysis 
## Study 1 Age
```{r}
#2015 Study 1 data
MTurk15 <- read.csv("~/MTurkOccDiversity/Demographics.csv", stringsAsFactors = FALSE)
names(MTurk15) <- c("country", "country text", "age", "gender", "years of current employment", "education level", "is english your primary language", "job title", "job title 2", "part time or full time", "sector", "employment status", "is MTurk primary income", "income currency", "approx annual income", "work hours per week", "ethnicity", "none")

#Chris's 2015 age analysis 
require(dplyr)
require(readxl)

#Load BLS Data
BLS_age_15 <- read_excel("BLS.Age.2015.xlsx")
